### 2020-07-27 draft.Rmd
dynamic p-values

```{r 2-sample}
x = list(nonseed$balchange, seed_accounts$balchange)
pFligPoli(x, method="Monte Carlo")
```

@@

A p-value of 0.0001 for the Fligner-Policello Test means that we reject the null hypothesis in favor of the alternate. We conclude that the median savings for SEED accounts is higher an for non-SEED accounts.

A p-value of 0 for the Tukey HSD permutation test leads us to reject the null hypothesis in favor of the alternative. We conclude that there is a difference in savings between at least two of the groups.

>>>>

```{r 2-sample}
x = list(nonseed$balchange, seed_accounts$balchange)
fp_result = pFligPoli(x, method="Monte Carlo")
fp_result
```

@@

A p-value of `r fp_result$p.val` for the Fligner-Policello Test means that we reject the null hypothesis in favor of the alternate. We conclude that the median savings for SEED accounts is higher an for non-SEED accounts.

A p-value of `r p_val` for the Tukey HSD permutation test leads us to reject the null hypothesis in favor of the alternative. We conclude that there is a difference in savings between at least two of the groups.
